---
title: "R Notebook"
output: html_notebook
---
https://rpubs.com/collnell/manova

Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Ctrl+Shift+Enter*. 
Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.


```{r}
install.packages('vegan')
library(vegan) 

```
```{r}
birds<-read.csv('https://raw.githubusercontent.com/collnell/lab-demo/master/bird_by_fg.csv')
trees<-read.csv('https://raw.githubusercontent.com/collnell/lab-demo/master/tree_comp.csv')
```


```{r}
birds
```
```{r}
trees
```

so we have bird species vs  diversity of trees where diversity of trees is presented as categorical variable - P or d

P/D - bird species
in birds we also have plot column that as far as I understand describes what tree species are there - in order to decode number to the tree species combination we have trees table


so we are intrested in B  of tree column - so we changed it as factor ...
```{r}
as.matrix(birds[,3:9]) #so we are dropping first two and last two columns 
experim<- merge(birds[,3:9], as.factor(trees$B))
experim[,1:7]
                
```
Original
```{r}
bird.matrix<-as.matrix(birds[,3:9])##response variables in a sample x species matrix
trees$B<-as.factor(trees$B)

bird.manova<-manova(bird.matrix~as.factor(B), data=trees) ##manova test
summary(bird.manova) 
```

My - we do not need to specify thios data !!!

```{r}
bird.matrix<-as.matrix(birds[,3:9])##response variables in a sample x species matrix
trees$B<-as.factor(trees$B)

ff<- as.matrix(experim[,1:7])

bird.manova<-manova(bird.matrix ~ trees$B) ##manova test
summary(bird.manova) 

```
```{r}
experim
```


# Permanova

so before permanova it is good practice to square root the dataset to reduce influeance of most abundant groups

```{r}
bird.mat<-sqrt(bird.matrix)#square root transform
bird.mat
```



Quantify pairwise compositional dissimilarity between sites based on species occurances.
- Bray-Curtis dissimilarity (abundance weighted)
- Jaccard (presence/absence)
- Gower’s (non-continuous variables)

so in case of true false matrix we will use jaccard
https://www.rdocumentation.org/packages/vegan/versions/2.4-2/topics/vegdist

```{r}
bird.dist<-vegdist(bird.mat, method='bray')


set.seed(36) #reproducible results

bird.div<-adonis2(bird.dist~DIVERSITY, data=birds, permutations = 999, method="bray")
bird.div


```
```{r}
bird.dist<-vegdist(bird.mat, method='bray')


set.seed(36) #reproducible results

bird.div<-adonis2(bird.dist~birds[['DIVERSITY']], permutations = 999, method="bray")
bird.div
```


```{r}
dispersion<-betadisper(bird.dist, group=birds$DIVERSITY)
permutest(dispersion)
```


```{r}
plot(dispersion, hull=FALSE, ellipse=TRUE) ##sd ellipse

```























