---
title: "week 4 programming"
output: html_notebook
---


Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Ctrl+Shift+Enter*. 
Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

```{r}
library(tidyverse)
```



```{r}
## Read outcome data
## Check that state and outcome are valid
## Return hospital name in that state with lowest 30-day death
## rate
best <- function(state, outt ) {
  if( state %in%  outcome_of_care_measures$State){

    
     outcome_of_care_measures %>% add_column(ha = parse_number(outcome_of_care_measures[[outt]]))  %>% arrange(ha,`Hospital Name`) %>% filter(State ==state ) %>% select(`Hospital Name`,outt,ha )


  }
  else{
    stop("invalid state")
    
  }
}

best("AK", "Hospital 30-Day Death (Mortality) Rates from Pneumonia" )
##`Hospital 30-Day Death (Mortality) Rates from Heart Attack`
##`Hospital 30-Day Death (Mortality) Rates from Heart Failure`
##`Hospital 30-Day Death (Mortality) Rates from Pneumonia`

```



##best("MD", "heart attack", outcome)
zz <- paste("Hospital 30-Day Death (Mortality) Rates from ","heart attack" )


outcome %>% filter(State == "TX" ) %>% mutate (ha = parse_number(`Hospital 30-Day Death (Mortality) Rates from Heart Attack`)) %>% arrange(ha) %>% select(`Hospital Name`,ha )


`Hospital 30-Day Death (Mortality) Rates from Heart Attack`
`Hospital 30-Day Death (Mortality) Rates from Heart Failure`
`Hospital 30-Day Death (Mortality) Rates from Pneumonia`

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
```{r}
outcome_of_care_measures 

```



```{r}
rankhospital <- function(state, outt, num = "best") {
## Read outcome data
## Check that state and outcome are valid
## Return hospital name in that state with the given rank
## 30-day death rate
  outcome_of_care_measures %>% add_column(ha = parse_number(outcome_of_care_measures[[outt]]))  %>% filter(State ==state ) %>% arrange(ha,`Hospital Name`) %>% select(`Hospital Name`,outt,ha )
  
}
rankhospital("TX", "Hospital 30-Day Death (Mortality) Rates from Pneumonia" , outcome)


```


```{r}
rankall <- function(outt, numm ) {
## Read outcome data
## Check that state and outcome are valid
## Return hospital name in that state with the given rank
## 30-day death rate   %>% filter(ha ==numm )
  outcome_of_care_measures %>% add_column(ha = parse_number(outcome_of_care_measures[[outt]]))  %>% arrange(desc(ha)) %>% select(State,`Hospital Name`,outt,ha )
  
}
rankall( "Hospital 30-Day Death (Mortality) Rates from Heart Attack" , 20)


```























