---
title: "Lexical Scoping"
output: html_notebook
---

Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Ctrl+Shift+Enter*. 
Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.


makeCacheMatrix: This function creates a special "matrix" object that can cache its inverse.
```{r}
makematrix <- function(x ) {
        i <- NULL
        set <- function(y) {
                x <<- y
                i <<- NULL
        }
        get <- function() x
        setinverse <- function(inv) i <<- inv
        getinverse <- function() i
        list(set = set, get = get,
             setinverse = setinverse,
             getinverse = getinverse)
}
```

cacheSolve: This function computes the inverse of the special "matrix" returned by makeCacheMatrix above. If the inverse has already been calculated (and the matrix has not changed), then the cachesolve should retrieve the inverse from the cache
Computing the inverse of a square matrix can be done with the solve function in R. For example, if X is a square invertible matrix, then solve(X) returns its inverse.

For this assignment, assume that the matrix supplied is always invertible.
```{r}
cacheInverse <- function(x, ...) {
        i <- x$getinverse()
        if(!is.null(i)) {
                message("getting cached data")
                return(i)
        }
        data <- x$get()
        i <- solve(data, ...)
        x$setinverse(i)
        i
}
```


Testing
```{r}
makeVector(3)$get()


```


